Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Update html and added comments for next steps.
modifying text

av.mov.rate <- 2
max.x <- 20

@@

weib.fits
```
Bootstrapping?
```{r}
weib.boot <- NULL

for(j in 1:10){
      s.df <- df %>% drop_na(s.id) %>%
      group_by(indiv) %>%
      sample_n(., 50)

@@

for(j in 1:10){
      s.df <- df %>% drop_na(s.id) %>%
      sample_n(., 50)

@@

 **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
 Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach.

>>>>

av.mov.rate <- 1
max.x <- 10

@@

weib.fits
```

Bootstrapping?  
Since there are hundreds or thousands of seeds getting dispersed between all the simulations, we will randomly sample seeds and fit a weibull distribution to generate the seed dispersal kernels. The visualization shows the parameters estimated for each bootstrap, for each individual (no pooling) or when we pool all the seed dispersal data (complete pooling).
```{r}
n.boots <- 10
samp.size <- 30
weib.boot <- NULL

for(j in 1:n.boots){
      s.df <- df %>% drop_na(s.id) %>%
      group_by(indiv) %>%
      sample_n(., samp.size)

@@

for(j in 1:n.boots){
      s.df <- df %>% drop_na(s.id) %>%
      sample_n(., samp.size)

@@

 **NEXT** Instead of the violin plots, I should show the dispersal kernels created by each of these bootstrap replicates.   
 Also, seems like for simulations, we need to sample 5 individuals multiple times, or sample more than 5 individuals from each population. I like the second approach because it resembles just sampling more individuals in the field, increasing your sample size to get a better picture of nature.
 Also, edit colors in violin plots to show each individuals color, and only use the one that includes the population as well. Leave population in black. Change red lines and dot to black too.
